CENSE - Perceptual test II

### 2019-02-26 report.tex
Proof read

This report presents the results of a perceptual experiment conducted as part of the Cense project~\footnote{\url{http://cense.ifsttar.fr/}}. From recordings of a sensor network with low information content, this study aims at proposing a processing chain for the estimation of the pleasantness in urban sound environments.

@@

The 19 scenes are then replicated using simScene~\cite{rossignol2015} with a database of extracts from recordings of isolated sound sources. This database is constructed from part of the LibriSpeech~\cite{panayotov2015} corpus for voices and Freesound\footnote{\url{https://freesound.org}} contributions for all other sources. For this experiment, the playback sound level is the same as during recordings of the references scenes, and ranges from 63.9~dB to 79.4~dB.\\

>>>>

This report presents the results of a perceptual experiment conducted as part of the Cense project~\footnote{\url{http://cense.ifsttar.fr/}}. From recordings of a sensor network with low information content, this study aims at proposing a processing chain for the estimation of pleasantness in urban sound environments.

@@

The 19 scenes are then replicated using simScene~\cite{rossignol2015} with a database of extracts from recordings of isolated sound sources. This database is constructed from part of the LibriSpeech~\cite{panayotov2015} corpus for voices and Freesound\footnote{\url{https://freesound.org}} contributions for all other sources. For this experiment, the playback sound level is the same as during recordings of the reference scenes, and ranges from 63.9~dB to 79.4~dB.\\
